Supplementary Figures relative to the SVA-DEA benchmark

### 2020-05-07 supplementary_figures/imputation.Rmd
move some main figures to the supplementary

```{r}
res <- readRDS("../data/results_imputation.rds")
dr <- res$dr
dr <- dr[order(rowMeans(dr>0,na.rm=TRUE)+rowMedians(dr, na.rm=TRUE), decreasing=TRUE),order(colMeans(dr,na.rm=TRUE),decreasing=TRUE)]
ds <- factor(sapply(strsplit(colnames(dr),"\\."),FUN=function(x) x[[1]]))
cols <- getQualitativePalette(length(unique(ds)))
names(cols) <- sort(unique(ds))
dsa <- ComplexHeatmap::HeatmapAnnotation(dataset=ds, col=list(dataset=cols), show_annotation_name = FALSE, show_legend=TRUE)

@@

ll2 <- list( "mean ARI"=mycast(ag, "ARI"),
            "ARI at true\nnb clusters"=mycast(ag2, "ARI"),
            "Mean precision"=mycast(ag, "mean_pr"),
            "Mean recall"=mycast(ag, "mean_re")
            )

@@

p2 <- grid.grabExpr(draw( myh(names(ll2)[1]) + myh(names(ll2)[2]) + 
                            myh(names(ll2)[3]) + myh(names(ll2)[4]) ))
```

```{r imputation, fig.width=10, fig.height=7}
pdf("imputation.pdf", width = 10, height=7)
plot_grid( p1, p2, nrow=2, labels=LETTERS[1:2], rel_heights = c(4.5,6))
dev.off()

plot_grid( p1, p2, nrow=2, labels=LETTERS[1:2], rel_heights = c(4,6))
```

**A:** Average silhouette width per subpopulation across various denoising/imputation methods. **B:** Clustering accuracy across denoising/imputation methods.

>>>>

```{r, include=FALSE}
if(!exists('FIG_NB')){
  FIG_NB <- 0
  getFigNb <- function(increment=FALSE){
    if(increment) FIG_NB <<- FIG_NB + 1
    FIG_NB
  }
}
```

# Supplementary Figure `r getFigNb(TRUE)`

```{r, include=FALSE}
res <- readRDS("../data/results_imputation.rds")
dr <- res$dr
dr <- dr[order(rowMeans(dr>0,na.rm=TRUE)+rowMedians(dr, na.rm=TRUE), decreasing=TRUE),order(colMeans(dr,na.rm=TRUE),decreasing=TRUE)]
ds <- factor(sapply(strsplit(colnames(dr),"\\."),FUN=function(x) x[[1]]))
cols <- getQualitativePalette(length(unique(ds)))
names(cols) <- sort(unique(ds))
dsa <- ComplexHeatmap::HeatmapAnnotation(dataset=ds, col=list(dataset=cols), show_annotation_name = FALSE, show_legend=TRUE)

@@

ll2 <- list( "mean ARI"=mycast(ag, "ARI"),
            "ARI at true\nnb clusters"=mycast(ag2, "ARI"),
            "Mean precision"=mycast(ag, "mean_pr")
            )

@@

p2 <- grid.grabExpr(draw( myh(names(ll2)[1]) + myh(names(ll2)[2]) + 
                            myh(names(ll2)[3]) ))
```

```{r imputation, fig.width=8.5, fig.height=7}
plot_grid( p1, p2, nrow=2, labels=LETTERS[1:2], rel_heights = c(4,6))
```

### Supplementary Figure `r getFigNb()`
**Evaluation of imputation/denoising methods.** Average silhouette width (**A**) and clustering accuracy (**B**) with or without (indicated as _none_) application of a denoising/imputation method.

### 2020-05-07 supplementary_figures/supp2_filtering.Rmd
move some main figures to the supplementary

>>>>

```{r, fig.height=4, fig.width=7}
res <- readRDS("../data/filtering_intermediateSummary.rds")
tmp <- res$filtering$pcCells
dbl <- 1+grepl("doublet",row.names(tmp))
row.names(tmp) <- paste0(c("","doublet + ")[dbl],sapply(strsplit(row.names(tmp)," "), FUN=function(x) x[2]))
cols <- colorRamp2( seq(from=0,to=sqrt(max(tmp)),length.out=100)^2,
                    colorRampPalette(c("white","red"))(100) )
draw(Heatmap(tmp, bottom_annotation=pipeComp:::.ds_anno(colnames(tmp)), 
        show_column_names = FALSE, cluster_columns=FALSE, show_row_dend=FALSE, 
        row_split=c("No doublet removal","Doublet removal")[dbl], 
        name="proportion\nexcluded", col=cols, heatmap_legend_param=list(
          at=c(0,5,10,30,60), labels=paste0(c(0,5,10,30,60),"%"),
          grid_height=unit(7,"mm")) ),
     merge_legend=TRUE)
```

Proportion of cells filtered out by subpopulation. Applying the filters in a cluster-wise fashion (using `scran::quickCluster`) leads to virtually no cell exclusion. The color-mapping is square-root transformed.

### 2020-05-07 supplementary_figures/supp3_normalization.Rmd
move some main figures to the supplementary

```{r}
suppressPackageStartupMessages({
  library(ggplot2)
  library(cowplot)
  library(ComplexHeatmap)
  library(reshape2)
  library(dplyr)
  library(viridis)
  library(pipeComp)
})
theme_set(theme_cowplot(font_size = 11))
source("../misc_functions.R")
```

@@

```{r covar, fig.width=8, fig.height=4.5}
res <- readRDS("../data/results_norm.rds")
H <- scrna_evalPlot_DR(res, "log10_total_counts", agg.by = "norm", anno_legend=FALSE, covar.type="mean")
H <- H + scrna_evalPlot_DR(res, "log10_total_features", agg.by = "norm", anno_legend=FALSE, covar.type="mean", reorder_rows = H)
H
```

@@

```{r}
res <- readRDS("../data/scVI.rds")
sil <- res$evaluation$dimreduction$silhouette$top_10_dims
sil$method <- factor(paste(sil$norm, sil$dr))
levels(sil$method) <- meths <- c("scVI.LD", "scran+seurat.pca", "scVI.LD", "scVI+seurat.pca","scVI.LD","sctransform")
levels(sil$dataset) <- c("Koh","Kumar","mixology10x3cl","mixology10x5cl","simMix1","simMix2","Zhengmix4eq","Zhengmix4uneq","Zhengmix8eq")
res$evaluation$dimreduction$silhouette$top_10_dims <- sil
x <- range(res$evaluation$dimreduction$silhouette$top_10_dims$meanSilWidth)
silColBreaks <- unique(round(c(x[1],0,x[2]/2,x[2]),1))
H <- scrna_evalPlot_DR(res, "meanSilWidth", scale=FALSE, agg.by = "method", 
                       reorder_rows=TRUE, value_format="", 
                       show_heatmap_legend=TRUE, anno_legend = TRUE, 
                       heatmap_legend_param=list(at=silColBreaks))

res$evaluation$clustering$method <- factor(paste(res$evaluation$clustering$norm, res$evaluation$clustering$dr))
res$evaluation$clustering$delta.nbClust <- res$evaluation$clustering$n_clus-res$evaluation$clustering$true.nbClusts
levels(res$evaluation$clustering$method) <- meths
meths <- levels(sil$method)[c(4,2,3,1)]
H2 <- scrna_evalPlot_clust(res, what="MI", agg.by="method", anno_legend=FALSE, reorder_rows=meths ) + 
  scrna_evalPlot_clust(res, what="ARI", agg.by="method", anno_legend=FALSE, reorder_rows=meths) + 
  scrna_evalPlot_clust(res, what="ARI", atTrueK = TRUE, agg.by="method", anno_legend=FALSE, reorder_rows=meths)
```

>>>>

```{r}
suppressPackageStartupMessages({
  library(ggplot2)
  library(cowplot)
  library(ComplexHeatmap)
  library(reshape2)
  library(dplyr)
  library(viridis)
  library(pipeComp)
})
theme_set(theme_cowplot(font_size = 11))
source("../misc_functions.R")

classifyNorms <- function(x){
  y <- rep("other", length(x))
  y[grep("sctransform",x)] <- "sctransform"
  y[grep("seurat",x)] <- "seurat"
  y[grep("scran",x)] <- "scran"
  y[grep("stableG",x)] <- "stableG"
  y
}
```

@@

```{r covar, fig.width=8, fig.height=4.5}
res <- readRDS("../data/results_norm.rds")
renameNorm(evalHeatmap(res, step="dimreduction", c("log10_total_counts","log10_total_features"), what2="meanAbsCorr.covariate2", agg.by = "norm", anno_legend=FALSE, row_split=classifyNorms(norm)))
```

@@

```{r}
res <- readRDS("../data/scVI.rds")
sil <- res$evaluation$dimreduction$silhouette$top_10_dims
sil$method <- factor(paste(sil$norm, sil$dr))
levels(sil$method) <- meths <- c("scVI.LD", "scran+seurat.pca", "scVI.LD", "scVI+seurat.pca","scVI.LD","sctransform")
levels(sil$dataset) <- c("Koh","Kumar","mixology10x3cl","mixology10x5cl","simMix1","simMix2","Zhengmix4eq","Zhengmix4uneq","Zhengmix8eq")
res$evaluation$dimreduction$silhouette$top_10_dims <- sil
x <- range(res$evaluation$dimreduction$silhouette$top_10_dims$meanSilWidth)
silColBreaks <- unique(round(c(x[1],0,x[2]/2,x[2]),1))
H <- scrna_evalPlot_silh(res, agg.by = "method", 
                       reorder_rows=TRUE, value_format="", 
                       show_heatmap_legend=TRUE, anno_legend = TRUE, 
                       heatmap_legend_param=list(at=silColBreaks))

res$evaluation$clustering$method <- factor(paste(res$evaluation$clustering$norm, res$evaluation$clustering$dr))
res$evaluation$clustering$delta.nbClust <- res$evaluation$clustering$n_clus-res$evaluation$clustering$true.nbClusts
levels(res$evaluation$clustering$method) <- meths
meths <- levels(sil$method)[c(4,2,3,1)]
H2 <- evalHeatmap(res, step="clustering", what=c("MI","ARI"), agg.by="method", anno_legend=FALSE, reorder_rows=meths ) + evalHeatmap(res, step="clustering", what="ARI", agg.by="method", anno_legend=FALSE, reorder_rows=meths, filterExpr = n_clus==true.nbClusts, name="ARI at true k", title="ARI at true k" )

```

### 2020-05-07 supplementary_figures/supp5_dr.Rmd
move some main figures to the supplementary

>>>>

```{r dimred, fig.width=10.5, fig.height=6}
res <- readRDS("../data/results_dimred2.rds")
H <- renameHrows(
  scrna_evalPlot_silh( res, reorder_rows=TRUE, 
                       heatmap_legend_param=list(direction="horizontal")),
  function(x) gsub("norm\\.","",x))
p1 <- grid.grabExpr(draw(H, heatmap_legend_side="bottom"))

p2 <- renameHrows(
  evalHeatmap( res, what=c("MI","min_pr"), agg.by=c("norm","dr"), reorder_rows=TRUE, anno_legend=FALSE,
               title=c("MI","Minimum precision")) + 
  evalHeatmap(res, what=c("ARI"), agg.by=c("norm","dr"), filterExpr=n_clus==true.nbClusts, 
              anno_legend=FALSE, title="ARI at true k"),
  function(x) gsub("norm\\.","",x)
)
p2 <- grid.grabExpr(draw(p2))

plot_grid(p1,p2, nrow=2, labels=LETTERS[1:2])
```

### Supplementary Figure `r getFigNb()`
Silhouette width (**A**) per subpopulation and clustering accuracy (**B**) according to various normalization and dimension reductions.
**Evaluation of common dimensionality reduction methods. A:** Minimum (left) and average (right) silhouette width per subpopulation resulting from combinations of normalization and dimension reductions. **B:** Clustering accuracy, measured by mutual information (MI), minimum subpopulation precision, and adjusted Rand index (ARI) at the true number of clusters.

### 2020-05-07 supplementary_figures/supp_figures.Rmd
updated many figures to improve readability...
move some main figures to the supplementary

---
title: \Large{pipeComp, a general framework for the evaluation of computational pipelines, reveals performant single-cell RNA-seq preprocessing tools}
subtitle: \vspace{0.2cm}\LARGE{Supplementary Figures}\vspace{0.3cm}
author:
- "Pierre-Luc Germain"
- "Anthony Sonrel"
- "Mark D. Robinson"
geometry: margin=1.5cm
output:
  pdf_document:
    toc: true
    fig_width: 8
    fig_height: 6
    citation_package: natbib
bibliography: ../bmc_article.bib
---

@@

@@

>>>>

---
title: \vspace{2cm}\Large{pipeComp, a general framework for the evaluation of computational pipelines, reveals performant single-cell RNA-seq preprocessing tools}
subtitle: \vspace{2cm}\LARGE{Supplementary Figures}\vspace{2cm}
date: "`r format(Sys.time(), '%d %B, %Y')`"
author:
- "Pierre-Luc Germain"
- "Anthony Sonrel"
- "Mark D. Robinson"
geometry: margin=1.5cm
output:
  pdf_document:
    fig_width: 8
    fig_height: 6
    citation_package: natbib
bibliography: ../bmc_article.bib
---

@@

# Supplementary Figure `r getFigNb(TRUE)`

```{r, fig.align="center", echo=FALSE, out.height="0.9\\textheight"}
knitr::include_graphics("dataset_description.pdf")
```

### Supplementary Figure `r getFigNb()`: Overview of the benchmark datasets

@@

```{r child='supp_svadea.Rmd'}
```

# Supplementary Figure `r getFigNb(TRUE)`

```{r, fig.align="center", echo=FALSE, out.height="0.8\\textheight"}
knitr::include_graphics("../main_figures/pipeComp_summary.pdf")
```

### Supplementary Figure `r getFigNb()`: Summary of the recommendations.

### 2020-05-07 supplementary_figures/supp_svadea.Rmd
move some main figures to the supplementary

```{r, fig.width=8, fig.height=9.5}
plot_grid(
  grid.grabExpr(draw(
    evalHeatmap(res1, what=c("logFC.pearson", "logFC.mad"), agg.by=c("sva.method","dea.method"), row_split="sva.method", font_factor=.9) +
      evalHeatmap(res1, what=c("TPR", "FDR"), agg.by=c("sva.method","dea.method"), row_split="sva.method", font_factor=.9,
                  filter=threshold==0.05)
  )),
  plotElapsed(res, agg.by=c("sva.method","dea.method")),
  nrow=2, labels=LETTERS[1:2]
)
```

@@

>>>>

@@

```{r, fig.width=8, fig.height=8.5}
plot_grid(
  grid.grabExpr(draw(
    evalHeatmap(res1, what=c("logFC.pearson", "logFC.mad"), agg.by=c("sva.method","dea.method"), row_split="sva.method", font_factor=.9) +
      evalHeatmap(res1, what=c("TPR", "FDR"), agg.by=c("sva.method","dea.method"), row_split="sva.method", font_factor=.9,
                  filter=threshold==0.05)
  )),
  plotElapsed(res, agg.by=c("sva.method","dea.method")),
  nrow=2, labels=LETTERS[1:2]
)
```
